Titeln på avhandlingens språk

### 2022-12-03 body/part1/overview.tex
restructuring again

\subsection{\cref{paper:olguinmunoz2018demoscaling}}\label{summary:2018demo}

@@

\subsection{\cref{paper:olguinmunoz2019edgedroid}}\label{summary:2019edgedroid}

@@

\section{A realistic model of human behavior in \acs{WCA}}\label{summary:model}

\subsection{\cref{paper:olguinmunoz2021impact}}\label{summary:2021impact}

@@

\FloatBarrier%
\subsection{\cref{paper:olguinmunoz2023realistic}}\label{summary:2023realistic}

\todo[inline]{Present the implementation of the model from \cref{paper:EdgeDroid2}}

@@

\subsubsection{Implications of the methodology for \ac{WCA} optimization}

@@

\FloatBarrier%
\section{Extending the methodology to \acsp{NCS}}

\subsection{\cref{paper:olguinmunoz2022cleave}}\label{summary:2022cleave}
\todo[inline]{\Cref{paper:olguinmunoz2022cleave} implements both the methodology and the tool.}

\subsection{The CLEAVE emulation framework}

\FloatBarrier%
\section{Orchestrating edge computing testbeds}

\subsection{\cref{paper:olguinmunoz2022ainur}}\label{summary:2022ainur}

>>>>

\subsection{Applying the methodology to \acs{WCA}}

\todo[inline]{\cref{paper:olguinmunoz2018demoscaling}}\label{summary:2018demo}

@@

@@

\todo[inline]{\cref{paper:olguinmunoz2019edgedroid}}\label{summary:2019edgedroid}

\subsection{Applying the methodology to \acsp{NCS}}
\todo[inline]{\Cref{paper:olguinmunoz2022cleave} implements both the methodology and the tool.}

\FloatBarrier%

\subsection{Orchestrating experimentation in edge computing testbeds}

\section{Extending the methodology in the context of \acs{WCA}}

\subsection{Characterizing human behavior}

@@

\subsection{Emulating human behavior}

@@

\section{Implications for the optimization of \ac{WCA}}

@@
